### 2024-11-12 IEEE template.tex
initial commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

	\title{ECE 551 Term Paper:\\Diagnostic and preventative devices for Alzheimer’s and Parkinson’s Diseases
	}

	\author{\IEEEauthorblockN{Brent Dickinson}
		\IEEEauthorblockN{Akash Mallula}
	}

	\maketitle

	\begin{abstract}
		This document is a model and instructions for \LaTeX.
		This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
		or Math in Paper Title or Abstract.
	\end{abstract}

	\begin{IEEEkeywords}
		component, formatting, style, styling, insert
	\end{IEEEkeywords}

	\section{Introduction}
	This document is a model and instructions for \LaTeX.
	Please observe the conference page limits.

	\section{Ease of Use}

	\subsection{Maintaining the Integrity of the Specifications}

	The IEEEtran class file is used to format your paper and style the text. All margins, 
	column widths, line spaces, and text fonts are prescribed; please do not 
	alter them. You may note peculiarities. For example, the head margin
	measures proportionately more than is customary. This measurement 
	and others are deliberate, using specifications that anticipate your paper 
	as one part of the entire proceedings, and not as an independent document. 
	Please do not revise any of the current designations.

	\section{Prepare Your Paper Before Styling}
	Before you begin to format your paper, first write and save the content as a 
	separate text file. Complete all content and organizational editing before 
	formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
	proofreading, spelling and grammar.

	Keep your text and graphic files separate until after the text has been 
	formatted and styled. Do not number text heads---{\LaTeX} will do that 
	for you.

	\subsection{Abbreviations and Acronyms}\label{AA}
	Define abbreviations and acronyms the first time they are used in the text, 
	even after they have been defined in the abstract. Abbreviations such as 
	IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
	abbreviations in the title or heads unless they are unavoidable.

	\subsection{Units}
	\begin{itemize}
		\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
		\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
		\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
		\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
	\end{itemize}

	\subsection{Equations}
	Number equations consecutively. To make your 
	equations more compact, you may use the solidus (~/~), the exp function, or 
	appropriate exponents. Italicize Roman symbols for quantities and variables, 
	but not Greek symbols. Use a long dash rather than a hyphen for a minus 
	sign. Punctuate equations with commas or periods when they are part of a 
	sentence, as in:
	\begin{equation}
		a+b=\gamma\label{eq}
	\end{equation}

	Be sure that the 
	symbols in your equation have been defined before or immediately following 
	the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
	the beginning of a sentence: ``Equation \eqref{eq} is . . .''

	\subsection{\LaTeX-Specific Advice}

	Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
	of ``hard'' references (e.g., \verb|(1)|). That will make it possible
	to combine sections, add equations, or change the order of figures or
	citations without having to go through the file line by line.

	Please don't use the \verb|{eqnarray}| equation environment. Use
	\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
	environment leaves unsightly spaces around relation symbols.

	Please note that the \verb|{subequations}| environment in {\LaTeX}
	will increment the main equation counter even when there are no
	equation numbers displayed. If you forget that, you might write an
	article in which the equation numbers skip from (17) to (20), causing
	the copy editors to wonder if you've discovered a new method of
	counting.

	{\BibTeX} does not work by magic. It doesn't get the bibliographic
	data from thin air but from .bib files. If you use {\BibTeX} to produce a
	bibliography you must send the .bib files.

	{\LaTeX} can't read your mind. If you assign the same label to a
	subsubsection and a table, you might find that Table I has been cross
	referenced as Table IV-B3.

	{\LaTeX} does not have precognitive abilities. If you put a
	\verb|\label| command before the command that updates the counter it's
	supposed to be using, the label will pick up the last counter to be
	cross referenced instead. In particular, a \verb|\label| command
	should not go before the caption of a figure or a table.

	Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
	will not stop equation numbers inside \verb|{array}| (there won't be
	any anyway) and it might stop a wanted equation number in the
	surrounding equation.

	\subsection{Some Common Mistakes}\label{SCM}
	\begin{itemize}
		\item The word ``data'' is plural, not singular.
		\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
		\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
		\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
		\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
		\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
		\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
		\item Do not confuse ``imply'' and ``infer''.
		\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
		\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
		\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
	\end{itemize}
	An excellent style manual for science writers is \cite{b7}.

	\subsection{Authors and Affiliations}
	\textbf{The class file is designed for, but not limited to, six authors.} A 
	minimum of one author is required for all conference articles. Author names 
	should be listed starting from left to right and then moving down to the 
	next line. This is the author sequence that will be used in future citations 
	and by indexing services. Names should not be listed in columns nor group by 
	affiliation. Please keep your affiliations as succinct as possible (for 
	example, do not differentiate among departments of the same organization).

	\subsection{Identify the Headings}
	Headings, or heads, are organizational devices that guide the reader through 
	your paper. There are two types: component heads and text heads.

	Component heads identify the different components of your paper and are not 
	topically subordinate to each other. Examples include Acknowledgments and 
	References and, for these, the correct style to use is ``Heading 5''. Use 
	``figure caption'' for your Figure captions, and ``table head'' for your 
	table title. Run-in heads, such as ``Abstract'', will require you to apply a 
	style (in this case, italic) in addition to the style provided by the drop 
	down menu to differentiate the head from the text.

	Text heads organize the topics on a relational, hierarchical basis. For 
	example, the paper title is the primary text head because all subsequent 
	material relates and elaborates on this one topic. If there are two or more 
	sub-topics, the next level head (uppercase Roman numerals) should be used 
	and, conversely, if there are not at least two sub-topics, then no subheads 
	should be introduced.

	\subsection{Figures and Tables}
	\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
	bottom of columns. Avoid placing them in the middle of columns. Large 
	figures and tables may span across both columns. Figure captions should be 
	below the figures; table heads should appear above the tables. Insert 
	figures and tables after they are cited in the text. Use the abbreviation 
	``Fig.~\ref{fig}'', even at the beginning of a sentence.

	\begin{table}[htbp]
		\caption{Table Type Styles}
		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
				\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
				\cline{2-4} 
				\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
				\hline
				copy& More table copy$^{\mathrm{a}}$& &  \\
				\hline
				\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
			\end{tabular}
			\label{tab1}
		\end{center}
	\end{table}

	\begin{figure}[htbp]
		\centerline{\includegraphics{figures/fig1.png}}
		\caption{Example of a figure caption.}
		\label{fig}
	\end{figure}

	Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
	rather than symbols or abbreviations when writing Figure axis labels to 
	avoid confusing the reader. As an example, write the quantity 
	``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
	units in the label, present them within parentheses. Do not label axes only 
	with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
	\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
	quantities and units. For example, write ``Temperature (K)'', not 
	``Temperature/K''.

	\section*{Acknowledgment}

	The preferred spelling of the word ``acknowledgment'' in America is without 
	an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
	G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
	acknowledgments in the unnumbered footnote on the first page.

	\section*{References}

	Please number citations consecutively within brackets \cite{b1}. The 
	sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
	number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
	the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

	Number footnotes separately in superscripts. Place the actual footnote at 
	the bottom of the column in which it was cited. Do not put footnotes in the 
	abstract or reference list. Use letters for table footnotes.

	Unless there are six authors or more give all authors' names; do not use 
	``et al.''. Papers that have not been published, even if they have been 
	submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
	that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
	Capitalize only the first word in a paper title, except for proper nouns and 
	element symbols.

	For papers published in translation journals, please give the English 
	citation first, followed by the original foreign-language citation \cite{b6}.

	\begin{thebibliography}{00}
		\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
		\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
		\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
		\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
		\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
		\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
		\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
	\end{thebibliography}
	\vspace{12pt}
	\color{red}
	IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-11-12 paper.tex
initial commit

--- 2024-11-12 IEEE template.tex
@@
 
-	\title{ECE 551 Term Paper:\\Diagnostic and preventative devices for Alzheimer’s and Parkinson’s Diseases
+	\title{ECE 590 Term Project
 	}
@@
 	\author{\IEEEauthorblockN{Brent Dickinson}
-		\IEEEauthorblockN{Akash Mallula}
+		\IEEEauthorblockN{Tianci}
 	}
@@
 	\begin{abstract}
-		This document is a model and instructions for \LaTeX.
-		This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-		or Math in Paper Title or Abstract.
+		Abstract here.
 	\end{abstract}
 
-	\begin{IEEEkeywords}
-		component, formatting, style, styling, insert
-	\end{IEEEkeywords}
+	\section{Introduction}
+	Text
 
-	\section{Introduction}
-	This document is a model and instructions for \LaTeX.
-	Please observe the conference page limits.
-
-	\section{Ease of Use}
-
-	\subsection{Maintaining the Integrity of the Specifications}
-
-	The IEEEtran class file is used to format your paper and style the text. All margins, 
-	column widths, line spaces, and text fonts are prescribed; please do not 
-	alter them. You may note peculiarities. For example, the head margin
-	measures proportionately more than is customary. This measurement 
-	and others are deliberate, using specifications that anticipate your paper 
-	as one part of the entire proceedings, and not as an independent document. 
-	Please do not revise any of the current designations.
-
-	\section{Prepare Your Paper Before Styling}
-	Before you begin to format your paper, first write and save the content as a 
-	separate text file. Complete all content and organizational editing before 
-	formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-	proofreading, spelling and grammar.
-
-	Keep your text and graphic files separate until after the text has been 
-	formatted and styled. Do not number text heads---{\LaTeX} will do that 
-	for you.
-
-	\subsection{Abbreviations and Acronyms}\label{AA}
-	Define abbreviations and acronyms the first time they are used in the text, 
-	even after they have been defined in the abstract. Abbreviations such as 
-	IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-	abbreviations in the title or heads unless they are unavoidable.
-
-	\subsection{Units}
-	\begin{itemize}
-		\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-		\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-		\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-		\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-	\end{itemize}
-
-	\subsection{Equations}
-	Number equations consecutively. To make your 
-	equations more compact, you may use the solidus (~/~), the exp function, or 
-	appropriate exponents. Italicize Roman symbols for quantities and variables, 
-	but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-	sign. Punctuate equations with commas or periods when they are part of a 
-	sentence, as in:
+	\section{Section 1}
+	Text
+	\subsection{Section A}
+	Text. Equation:
 	\begin{equation}
@@
 	\end{equation}
-
-	Be sure that the 
-	symbols in your equation have been defined before or immediately following 
-	the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-	the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-	\subsection{\LaTeX-Specific Advice}
-
-	Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-	of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-	to combine sections, add equations, or change the order of figures or
-	citations without having to go through the file line by line.
-
-	Please don't use the \verb|{eqnarray}| equation environment. Use
-	\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-	environment leaves unsightly spaces around relation symbols.
-
-	Please note that the \verb|{subequations}| environment in {\LaTeX}
-	will increment the main equation counter even when there are no
-	equation numbers displayed. If you forget that, you might write an
-	article in which the equation numbers skip from (17) to (20), causing
-	the copy editors to wonder if you've discovered a new method of
-	counting.
-
-	{\BibTeX} does not work by magic. It doesn't get the bibliographic
-	data from thin air but from .bib files. If you use {\BibTeX} to produce a
-	bibliography you must send the .bib files.
-
-	{\LaTeX} can't read your mind. If you assign the same label to a
-	subsubsection and a table, you might find that Table I has been cross
-	referenced as Table IV-B3.
-
-	{\LaTeX} does not have precognitive abilities. If you put a
-	\verb|\label| command before the command that updates the counter it's
-	supposed to be using, the label will pick up the last counter to be
-	cross referenced instead. In particular, a \verb|\label| command
-	should not go before the caption of a figure or a table.
-
-	Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-	will not stop equation numbers inside \verb|{array}| (there won't be
-	any anyway) and it might stop a wanted equation number in the
-	surrounding equation.
-
-	\subsection{Some Common Mistakes}\label{SCM}
+	Bullets:
 	\begin{itemize}
-		\item The word ``data'' is plural, not singular.
-		\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-		\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-		\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-		\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-		\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-		\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-		\item Do not confuse ``imply'' and ``infer''.
-		\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-		\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-		\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
+		\item Bullet 1.
+		\item Bullet 2.
 	\end{itemize}
-	An excellent style manual for science writers is \cite{b7}.
-
-	\subsection{Authors and Affiliations}
-	\textbf{The class file is designed for, but not limited to, six authors.} A 
-	minimum of one author is required for all conference articles. Author names 
-	should be listed starting from left to right and then moving down to the 
-	next line. This is the author sequence that will be used in future citations 
-	and by indexing services. Names should not be listed in columns nor group by 
-	affiliation. Please keep your affiliations as succinct as possible (for 
-	example, do not differentiate among departments of the same organization).
-
-	\subsection{Identify the Headings}
-	Headings, or heads, are organizational devices that guide the reader through 
-	your paper. There are two types: component heads and text heads.
-
-	Component heads identify the different components of your paper and are not 
-	topically subordinate to each other. Examples include Acknowledgments and 
-	References and, for these, the correct style to use is ``Heading 5''. Use 
-	``figure caption'' for your Figure captions, and ``table head'' for your 
-	table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-	style (in this case, italic) in addition to the style provided by the drop 
-	down menu to differentiate the head from the text.
-
-	Text heads organize the topics on a relational, hierarchical basis. For 
-	example, the paper title is the primary text head because all subsequent 
-	material relates and elaborates on this one topic. If there are two or more 
-	sub-topics, the next level head (uppercase Roman numerals) should be used 
-	and, conversely, if there are not at least two sub-topics, then no subheads 
-	should be introduced.
-
-	\subsection{Figures and Tables}
-	\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-	bottom of columns. Avoid placing them in the middle of columns. Large 
-	figures and tables may span across both columns. Figure captions should be 
-	below the figures; table heads should appear above the tables. Insert 
-	figures and tables after they are cited in the text. Use the abbreviation 
-	``Fig.~\ref{fig}'', even at the beginning of a sentence.
+	Figures and tables. Fig.~\ref{fig} shows X. Table ~\ref{tab1} shows Y.
 
@@
 
-	Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-	rather than symbols or abbreviations when writing Figure axis labels to 
-	avoid confusing the reader. As an example, write the quantity 
-	``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-	units in the label, present them within parentheses. Do not label axes only 
-	with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-	\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-	quantities and units. For example, write ``Temperature (K)'', not 
-	``Temperature/K''.
-
-	\section*{Acknowledgment}
-
-	The preferred spelling of the word ``acknowledgment'' in America is without 
-	an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-	G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-	acknowledgments in the unnumbered footnote on the first page.
-
 	\section*{References}
 
-	Please number citations consecutively within brackets \cite{b1}. The 
-	sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-	number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-	the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-	Number footnotes separately in superscripts. Place the actual footnote at 
-	the bottom of the column in which it was cited. Do not put footnotes in the 
-	abstract or reference list. Use letters for table footnotes.
-
-	Unless there are six authors or more give all authors' names; do not use 
-	``et al.''. Papers that have not been published, even if they have been 
-	submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-	that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-	Capitalize only the first word in a paper title, except for proper nouns and 
-	element symbols.
-
-	For papers published in translation journals, please give the English 
-	citation first, followed by the original foreign-language citation \cite{b6}.
-
+	Cite like this \cite{b1}.
 		\begin{thebibliography}{00}
@@
 529--551, April 1955.
-		\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-		\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-		\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-		\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-		\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-		\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
 	\end{thebibliography}
-	\vspace{12pt}
-	\color{red}
-	IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2024-11-17 paper.tex
added outline to paper

@@
 \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 
-	\title{ECE 590 Term Project
-	}
+	\title{Integration of 75MW Solar PV Plant: Transmission System Design Analysis}
 
@@
 	\begin{abstract}
-		Abstract here.
+		This report presents the design and analysis of transmission system modifications required to integrate a new 75MW solar PV plant while addressing existing system reliability concerns.
+The study evaluates various transmission line and transformer options to determine the most cost-effective solution that maintains system stability under both normal and N-1 contingency conditions.
 	\end{abstract}
@@
 	\section{Introduction}
-	Text
+	\begin{itemize}
+		\item Project overview and objectives
+		\item System requirements and constraints
+		\item Design methodology
+	\end{itemize}
 
-	\section{Section 1}
-	Text
-	\subsection{Section A}
-	Text. Equation:
-	\begin{equation}
-		a+b=\gamma\label{eq}
-	\end{equation}
-	Bullets:
+	\section{Initial System Analysis}
+	\subsection{Base Case Evaluation}
 	\begin{itemize}
-		\item Bullet 1.
-		\item Bullet 2.
+		\item Existing system configuration
+		\item Current system performance metrics
+		\item Identification of existing violations
 	\end{itemize}
-	Figures and tables. Fig.~\ref{fig} shows X. Table ~\ref{tab1} shows Y.
 
+	\subsection{Contingency Analysis Results}
+	\begin{itemize}
+		\item N-1 contingency findings
+		\item Critical violations and their implications
+		\item Key problem areas identified
+	\end{itemize}
+
+	\section{Design Solutions}
+	\subsection{Design Options Considered}
+	\begin{itemize}
+		\item Transmission line alternatives
+		\item Voltage level considerations
+		\item Transformer placement options
+	\end{itemize}
+
+	\subsection{Technical Analysis}
+	\begin{itemize}
+		\item Power flow studies
+		\item Contingency analysis results
+		\item System performance improvements
+	\end{itemize}
+
+	\section{Economic Analysis}
+	\subsection{Cost Components}
+	\begin{itemize}
+		\item Fixed costs (lines, transformers, substations)
+		\item Variable costs (distance-based)
+		\item Loss reduction benefits
+	\end{itemize}
+
+	\subsection{Solution Comparison}
 	\begin{table}[htbp]
-		\caption{Table Type Styles}
+		\caption{Cost Comparison of Design Options}
 		\begin{center}
@@
 				\hline
-				\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-				\cline{2-4} 
-				\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+				\textbf{Design Option} & \textbf{Capital Cost} & \textbf{Loss Savings} & \textbf{Net Cost} \\
 				\hline
-				copy& More table copy$^{\mathrm{a}}$& &  \\
+				Option 1 & & & \\
 				\hline
-				\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+				Option 2 & & & \\
+				\hline
 			\end{tabular}
-			\label{tab1}
+			\label{tab:costs}
 		\end{center}
@@
 
-	\begin{figure}[htbp]
-		\centerline{\includegraphics{figures/fig1.png}}
-		\caption{Example of a figure caption.}
-		\label{fig}
-	\end{figure}
+	\section{Recommended Solution}
+	\begin{itemize}
+		\item Final design selection
+		\item Technical justification
+		\item Economic justification
+		\item Implementation considerations
+	\end{itemize}
 
-	\section*{References}
+	\section{Conclusion}
+	Summary of key findings and recommendations
 
-	Cite like this \cite{b1}.
 	\begin{thebibliography}{00}
-		\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
+		\bibitem{b1} PowerWorld Corporation, "PowerWorld Simulator Manual," 2024.
+		\bibitem{b2} IEEE Standard 1547-2018, "IEEE Standard for Interconnection and Interoperability of Distributed Energy Resources with Associated Electric Power Systems Interfaces."
 	\end{thebibliography}
+
 \end{document}

### 2024-11-17 paper.tex
work on initial system analysis

@@
 \section{Introduction}
-	\begin{itemize}
-		\item Project overview and objectives
-		\item System requirements and constraints
-		\item Design methodology
-	\end{itemize}
+The integration of renewable energy sources into existing power grids presents technical challenges.
+We analyze the design requirements and potential solutions for integrating a new 75 MW utility-scale solar photo-voltaic (PV) facility into an existing 37-bus power system while also solving current reliability issues.
+
+We aim to find the most cost-effective transmission system additions required to integrate 75 MW of solar generation at the NEWSOLAR substation.
+That goal is subordinate to the constraints of ensuring system reliability through dual transmission paths to the facility and resolving existing system violations identified using PowerWorld's contingency analysis.
+
+The design must satisfy the following constraints.
+Bus voltages must be maintained between 0.95 and 1.10 per unit, while keeping all line flows below 100\% of their thermal limits.
+The system must maintain stability under both normal operation and N-1 contingency conditions.
+Additionally, redundant transmission paths to the NEWSOLAR substation are required.
+The system must accommodate the solar plant operating at both full capacity (75 MW) and offline conditions.
+
+Our approach incorporates contingency analysis, evaluation of available transmission corridors and voltage levels, and assessment of various conductor types and their associated costs.
+We consider transformer options and substation modifications.
+We conduct an economic analysis incorporating both capital costs and five-year loss reduction benefits.
+
+Initial contingency analysis reveals specific reliability concerns in the OAK69-BUCKEYE69-APPLE69 corridor, which must be addressed alongside the integration of the new solar facility.
+The following sections detail the technical analysis, proposed solutions, and economic justification for the recommended design.
 
@@
 \subsection{Base Case Evaluation}
-	\begin{itemize}
-		\item Existing system configuration
-		\item Current system performance metrics
-		\item Identification of existing violations
-	\end{itemize}
+The existing 37-bus system operates with a total load of 826.3 MW and 275.5 Mvar, served by ten generators producing 837.7 MW.
+System losses are approximately 10.7 MW, representing 1.3\% of total generation, which indicates reasonably efficient power delivery under normal conditions.
+The system maintains adequate reactive power compensation through nine switched shunts, collectively providing -122.5 Mvar of reactive support.
 
-	\subsection{Contingency Analysis Results}
-	\begin{itemize}
-		\item N-1 contingency findings
-		\item Critical violations and their implications
-		\item Key problem areas identified
-	\end{itemize}
+PowerWorld's case summary for the existing system is shown in Figure \ref{fig:casesummaryexisting}
+\begin{figure}[tbph]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/case_summary_existing}
+	\caption{Case summary for existing system}
+	\label{fig:casesummaryexisting}
+\end{figure}
+\subsection{Contingency Analysis}
+PowerWorld's contingency analysis examines conditions when each element of the power system is taken offline.
+It reveals vulnerability in the 69 kV network in three contingency violations.
+Specifically, loss of either the PINE138 transformer or the PINE69-APPLE69 line results in overload, with the OAK69-BUCKEYE69 line experiencing loading up to 110.8\% of its thermal limit.
+These violations suggest that the existing infrastructure is approaching its capacity limits.
 
+These results are summarized in Table \ref{tab:violations}. A zoomed-in view of the affected areas of the power system is shown in Figure \ref{fig:baseviolations}.
+\begin{table}[htbp]
+	\caption{Line violations in contingency analysis}
+	\begin{center}
+		\begin{tabular}{|l|c|c|c|}
+			\hline
+			\textbf{Contingency} & \textbf{Flow(A)} & \textbf{Limit(A)} & \textbf{\%} \\
+			\hline
+			\textit{PINE138-PINE69 Xfmr:} & & & \\
+			OAK69-BUCKEYE69 & 760.3 & 686.1 & 110.8 \\
+			BUCKEYE69-APPLE69 & 454.2 & 418.4 & 108.6 \\
+			\hline
+			\textit{PINE69-APPLE69 Line:} & & & \\
+			OAK69-BUCKEYE69 & 699.2 & 686.1 & 101.9 \\
+			\hline
+		\end{tabular}
+		\label{tab:violations}
+	\end{center}
+\end{table}
+\begin{figure}[tbph]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/base_violations}
+	\caption{Existing contingency violations - problem area}
+	\label{fig:baseviolations}
+\end{figure}
 \section{Design Solutions}

### 2024-11-24 paper.tex
added new scenarios

@@
 \end{figure}
-\section{Design Solutions}
-\subsection{Design Options Considered}
-\begin{itemize}
-	\item Transmission line alternatives
-	\item Voltage level considerations
-	\item Transformer placement options
-\end{itemize}
+\section{Design}
+The design solution must incorporate new transmission infrastructure to connect the 75 MW solar facility at NEWSOLAR while simultaneously addressing existing problems.
+There must be redundant transmission paths to NEWSOLAR for reliability, meaning at least two separate transmission lines must be constructed.
+These lines can be either 69 kV or 138 kV, with NEWSOLAR and all existing substations capable of accommodating either voltage level through installation of transformers.
+The system must maintain all bus voltages between 0.95 and 1.10 per unit and keep all line flows below their thermal limits under both normal operation and any single-contingency (N-1) scenario.
 
-\subsection{Technical Analysis}
-\begin{itemize}
-	\item Power flow studies
-	\item Contingency analysis results
-	\item System performance improvements
-\end{itemize}
+The optimal solution will minimize total cost, calculated as the construction costs minus any savings from reduced system losses over a 5-year period at \$60/MWh.
+Construction costs include both fixed components (\$1.25M for 138 kV or \$750k for 69 kV lines) and variable costs based on distance and conductor type.
+If 138 kV is utilized, additional costs include substation upgrades (\$900k per substation) and necessary transformers (\$1.5M for 101 MVA or \$1.8M for 168 MVA).
+The solution must resolve existing contingency violations, particularly the overloads observed in the OAK69-BUCKEYE69-APPLE69 corridor, while ensuring reliable operation both when the solar plant is at full output and when it is offline.
+\subsection{Transmission Line Parameters}
+A note on how to input transmission line parameters into PowerWorld is in order.
+Table A.4 in the text gives resistance in ohms per conductor per mile for 50$^\circ$C at 60Hz as well as series inductance (ohms/mile/conductor for 1 foot spacing) and shunt capacitance (Mohms/mile/conductor for 1 foot spacing).
+Resistance pulled from Table A.4 can be input directly into the "Calculate Impedances" dialog box in PowerWorld.
+But for 69kV lines, the three phases are spaced 2m apart and 4m apart for 138kV lines.
+We need a way to convert the 1-foot spacing parameters appropriately.
+Assuming equilateral spacing of lines, Equation 4.5.9 in the text suggests a simple way to adjust series inductance.
+We simply add the following quantity to that given in the table:
+\begin{flalign}
+	\Delta L_{69} &= 2\pi\cdot60\cdot2\times10^{-7}\left(\ln\frac{D_2}{D_1}\right)\nonumber\\
+	&= 2\pi\cdot60\cdot2\times10^{-7}\left(\ln\frac{2}{0.3048}\right) = 0.0001\\
+	\Delta L_{138} &= 2\pi\cdot60\cdot2\times10^{-7}\left(\ln\frac{4}{0.3048}\right) = 0.0002.
+\end{flalign}
 
-\section{Economic Analysis}
-\subsection{Cost Components}
-\begin{itemize}
-	\item Fixed costs (lines, transformers, substations)
-	\item Variable costs (distance-based)
-	\item Loss reduction benefits
-\end{itemize}
+Using Equation 4.9.15 in the text we can develop a multiplication factor to adjust table shunt capacitance values for larger conductor spacing:
+\begin{flalign}
+	\frac{X_c^\text{new}}{X_c^\text{old}} & = \frac{\ln\left(\frac{D_\text{old}}{r}\right)}{\ln\left(\frac{D_\text{new}}{r}\right)}
+\end{flalign}
 
-\subsection{Solution Comparison}
-\begin{table}[htbp]
-	\caption{Cost Comparison of Design Options}
-	\begin{center}
-		\begin{tabular}{|c|c|c|c|}
+where $r$ is the conductor's outer radius. Though these are stranded conductors, we treat them as solid since the associated error is small.
+\subsection{Candidate Solutions}
+With an impractically large set of possible solutions, we started with a couple of simple approaches to integrate the 75 MW solar facility while addressing system reliability concerns.
+We focused mainly on distance from NEWSOLAR, identifying BUCKEYE and APPLE as the closest stations.
+
+First we attempted to maintain NEWSOLAR at 69kV with new connections to BUCKEYE and APPLE using Condor 900A/107.5MVA conductors.
+We selected those stations because of their proximity to NEWSOLAR (only 6km each).
+We upgraded the OAK69-BUCKEYE69 and BUCKEYE69-APPLE69 lines to the highest-rated available 69kV conductor (Condor at 900A).
+However, contingency analysis revealed voltage violations at OAK138, dropping to 0.939 per unit when the OAK345-OAK138 transformer is opened.
+This suggests a need for stronger integration with the 138kV network.
+
+Next we installed a 138kV bus at NEWSOLAR with a 138/69kV transformer connecting it to the 69kV bus.
+Since voltage dropped too low at OAK in the previous design, we connected NEWSOLAR138 to OAK138 using Cardinal 1010A/241.4MVA lines.
+Since 138kV lines are significantly more expensive than 69kV, we kept the 69kV connection to PINE69.
+We found a slight overcurrent contingency violation on the OAK69-BUCKEYE69 line when PINE-APPLE is open, so we upgraded it to the 900A Condor lines.
+With this new configuration there are no contingency violations.
+
+PowerWorld's Case Summary for this configuration shows losses of 10.9MW, a 0.2MW increase from the base scenario.
+That suggests we should consider upgrading more transmission lines to see if we can achieve enough reduction in loss to offset costs.
+Contingency analysis showed no violations with this configuration, so we now examine the cost of this approach before considering more upgrades.
+Table \ref{tab:cost_breakdown_with_losses} shows the breakdown of costs incurred, with a total of \$21,715,600.
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{|l|r|}
 		\hline
-			\textbf{Design Option} & \textbf{Capital Cost} & \textbf{Loss Savings} & \textbf{Net Cost} \\
-			\hline
-			Option 1 & & & \\
-			\hline
-			Option 2 & & & \\
-			\hline
+		\textbf{Modification} & \textbf{Cost (\$)} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Replace OAK-BUCKEYE (69kV Condor)}} \\ 
+		\hspace{1em} Fixed Cost & 750,000 \\ 
+		\hspace{1em} Variable Cost (\$410,000/km for 8 km) & 3,280,000 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{4,030,000} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{138-kV Bus/101MVA Transformer}} \\ 
+		\hspace{1em} Bus & 900,000 \\ 
+		\hspace{1em} Transformer & 1,500,000 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{2,400,000} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-OAK138 (138kV Cardinal)}} \\ 
+		\hspace{1em} Fixed Cost & 1,250,000 \\ 
+		\hspace{1em} Variable Cost (\$540,000/km for 13 km) & 7,020,000 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{8,270,000} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-PINE69 (69kV Condor)}} \\ 
+		\hspace{1em} Fixed Cost & 750,000 \\ 
+		\hspace{1em} Variable Cost (\$410,000/km for 14 km) & 5,740,000 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{6,490,000} \\ \hline
+		\textbf{Increased Loss (0.2 MW over 5 years)} & \textbf{525,600} \\ \hline
+		\textbf{Grand Total} & \textbf{21,715,600} \\ \hline
 	\end{tabular}
-		\label{tab:costs}
-	\end{center}
+	\vspace{0.5em}
+	\caption{Cost Breakdown of Option 2}
+	\label{tab:cost_breakdown_with_losses}
 \end{table}
 
-\section{Recommended Solution}
-\begin{itemize}
-	\item Final design selection
-	\item Technical justification
-	\item Economic justification
-	\item Implementation considerations
-\end{itemize}
-
+The massive expense of replacing lines seen in Table \ref{tab:cost_breakdown_with_losses} suggests that loss reduction will not pay for more line upgrades.
+Next we examine whether there is a better way to connect NEWSOLAR to the grid, perhaps with closer stations.
 \section{Conclusion}

### 2024-11-24 paper.tex
added scenarios

@@
 
-PowerWorld's Case Summary for this configuration shows losses of 10.9MW, a 0.2MW increase from the base scenario.
-That suggests we should consider upgrading more transmission lines to see if we can achieve enough reduction in loss to offset costs.
-Contingency analysis showed no violations with this configuration, so we now examine the cost of this approach before considering more upgrades.
-Table \ref{tab:cost_breakdown_with_losses} shows the breakdown of costs incurred, with a total of \$21,715,600.
+PowerWorld's Case Summary for this configuration shows losses of 10.6MW, a 0.1MW decrease from the base scenario.
+That will slightly offset upgrade costs from power saving over five years.
+Contingency analysis showed no violations with this configuration, so we now examine the cost of this approach.
+Table \ref{tab:cost_breakdown_option1} shows the breakdown of costs incurred, with a total of \$20,927,200.
 \begin{table}[h!]
@@
 		\hspace{1em} \textbf{Total} & \textbf{6,490,000} \\ \hline
-		\textbf{Increased Loss (0.2 MW over 5 years)} & \textbf{525,600} \\ \hline
-		\textbf{Grand Total} & \textbf{21,715,600} \\ \hline
+		\textbf{Loss Savings (0.1 MW over 5 years)} & \textbf{-262,800} \\ \hline
+		\textbf{Grand Total} & \textbf{20,927,200} \\ \hline
 	\end{tabular}
 	\vspace{0.5em}
-	\caption{Cost Breakdown of Option 2}
-	\label{tab:cost_breakdown_with_losses}
+	\caption{Cost Breakdown of Transmission Line and Transformer Upgrades, Including Loss Savings}
+	\label{tab:cost_breakdown_option1}
 \end{table}
 
-The massive expense of replacing lines seen in Table \ref{tab:cost_breakdown_with_losses} suggests that loss reduction will not pay for more line upgrades.
+The massive expense of replacing lines seen in Table \ref{tab:cost_breakdown_option1} suggests that loss reduction will not pay for more line upgrades.
 Next we examine whether there is a better way to connect NEWSOLAR to the grid, perhaps with closer stations.

### 2024-12-06 paper.tex
few updates to report

@@
 A note on how to input transmission line parameters into PowerWorld is in order.
-Table A.4 in the text gives resistance in ohms per conductor per mile for 50$^\circ$C at 60Hz as well as series inductance (ohms/mile/conductor for 1 foot spacing) and shunt capacitance (Mohms/mile/conductor for 1 foot spacing).
-Resistance pulled from Table A.4 can be input directly into the "Calculate Impedances" dialog box in PowerWorld.
+Table A.4 in the text gives resistance in ohms per conductor per mile for 50$^\circ$C at 60Hz as well as series inductance (ohms/mile/conductor for 1 foot spacing) and shunt capacitance (S/mile/conductor for 1 foot spacing).
+Resistance pulled from Table A.4 can be used directly in the "Calculate Impedances" dialog box in PowerWorld.
 But for 69kV lines, the three phases are spaced 2m apart and 4m apart for 138kV lines.
 We need a way to convert the 1-foot spacing parameters appropriately.
-Assuming equilateral spacing of lines, Equation 4.5.9 in the text suggests a simple way to adjust series inductance.
-We simply add the following quantity to that given in the table:
+Assuming equilateral spacing of lines, Equation 4.5.9 in the text suggests a simple way to adjust series per-mile impedance from the table:
 \begin{flalign}
-	\Delta L_{69} &= 2\pi\cdot60\cdot2\times10^{-7}\left(\ln\frac{D_2}{D_1}\right)\nonumber\\
-	&= 2\pi\cdot60\cdot2\times10^{-7}\left(\ln\frac{2}{0.3048}\right) = 0.0001\\
-	\Delta L_{138} &= 2\pi\cdot60\cdot2\times10^{-7}\left(\ln\frac{4}{0.3048}\right) = 0.0002.
+	X_{2m} &= X_{1ft}\cdot\frac{\ln\left(\frac{2\times3.28}{\text{GMR}}\right)}{\ln\left(\frac{1}{\text{GMR}}\right)}
 \end{flalign}
+where GMR comes from the same table for the conductor of interest. We calculate shunt susceptance manually using values given in the table:
+\begin{flalign}
+	B_{2m} & = \frac{2\pi\epsilon}{\ln(D/r)}
+\end{flalign}
+where $r$ is the conductor's outer radius. Though these are stranded conductors, we treat them as solid since the associated error is small. Note that we multiply this value by 3 for 3 phases.
 
-Using Equation 4.9.15 in the text we can develop a multiplication factor to adjust table shunt capacitance values for larger conductor spacing:
-\begin{flalign}
-	\frac{X_c^\text{new}}{X_c^\text{old}} & = \frac{\ln\left(\frac{D_\text{old}}{r}\right)}{\ln\left(\frac{D_\text{new}}{r}\right)}
-\end{flalign}
-
-where $r$ is the conductor's outer radius. Though these are stranded conductors, we treat them as solid since the associated error is small.
+Table \ref{tab:tl_params} shows parameters for the 69kV lines which go into PowerWorld's Impedance Calculator. We do not include the 138kV lines for reasons explained in the next section.
+\begin{table}
+	\begin{tabular}{|l|c|c|c|}
+		\hline
+		Parameter & Rook & Crow & Condor \\
+		\hline
+		R ($\Omega$/mile) & 0.1688 & 0.1482 & 0.1378 \\
+		X ($\Omega$/mile) & 0.6421 & 0.6352 & 0.6326 \\
+		B (S/mile) & $16.15\times10^{-6}$ & $16.30\times10^{-6}$ & $16.44\times10^{-6}$ \\
+		\hline
+	\end{tabular}
+	\vspace{0.5em}
+	\caption{Transmission Line Parameters at 60 Hz, 2m Spacing}
+	\label{tab:tl_params}
+\end{table}
 \subsection{Candidate Solutions}
-With an impractically large set of possible solutions, we started with a couple of simple approaches to integrate the 75 MW solar facility while addressing system reliability concerns.
-We focused mainly on distance from NEWSOLAR, identifying BUCKEYE and APPLE as the closest stations.
+Table \ref{tab:all_conn} shows all possible NEWSOLAR connections to the network, given the provided set of right-of-way paths available to us.
+The cost of 138kV lines and transformers suggests we can eliminate any solution involving those lines; we will connect NEWSOLAR exclusively with 69kV lines unless we are unable to solve potential contingency violations.
+The approach here is to start with the solution involving least total line distance (case 1).
+We move to solutions involving longer connections only if we run into contingency violations.
+Further, we use the least expensive conductors to start and upgrade only if needed.
+\begin{table}[h]
+	\centering
+	\begin{tabular}{|c|l|c|}
+		\hline
+		\textbf{Case number} & \textbf{Destination buses} & \textbf{Total distance} \\
+		\hline
+		1 & BK69, AP69 & 12 \\
+		2 & BK69, OAK69 & 19 \\
+		3 & BK69, OAK138 & 19 \\
+		4 & AP69, OAK69 & 19 \\
+		5 & AP69, OAK138 & 19 \\
+		6 & BK69, PIINE69 & 20 \\
+		7 & BK69, PINE138 & 20 \\
+		8 & AP69, PINE69 & 20 \\
+		9 & AP69, PINE138 & 20 \\
+		10 & BK69, MP69 & 21 \\
+		11 & AP69, MP69 & 21 \\
+		12 & OAK69, PINE69 & 27 \\
+		13 & OAK69, PINE138 & 27 \\
+		14 & OAK138, PINE69 & 27 \\
+		15 & OAK138, PINE138 & 27 \\
+		16 & OAK69, MP69 & 28 \\
+		17 & OAK138, MP69 & 28 \\
+		18 & PINE69, MP69 & 29 \\
+		19 & PINE138, MP69 & 29 \\
+		\hline
+	\end{tabular}
+	\vspace{0.5em}
+	\caption{Possible NEWSOLAR Connections}
+	\label{tab:all_conn}
+\end{table}
+We started with case 1: maintain NEWSOLAR at 69kV with connections to BUCKEYE and APPLE using Rook 770A conductors.
 

### 2024-12-07 paper.tex
updates with correct parameters

@@
 \end{flalign}
-where GMR comes from the same table for the conductor of interest. We calculate shunt susceptance manually using values given in the table:
+where GMR comes from the same table for the conductor of interest.
+
+We calculate shunt susceptance similarly given the 1-foot spacing shunt reactance and outer diameter given in the table:
 \begin{flalign}
-	B_{2m} & = \frac{2\pi\epsilon}{\ln(D/r)}
+	B_{2m} & = \frac{\ln(1/r)}{Xc_{1ft}\cdot\ln(2\times3.28/r)}
 \end{flalign}
@@
 		X ($\Omega$/mile) & 0.6421 & 0.6352 & 0.6326 \\
-		B (S/mile) & $16.15\times10^{-6}$ & $16.30\times10^{-6}$ & $16.44\times10^{-6}$ \\
+		B (S/mile) & $6.63\times10^{-6}$ & $6.71\times10^{-6}$ & $6.78\times10^{-6}$ \\
 		\hline
@@
 The cost of 138kV lines and transformers suggests we can eliminate any solution involving those lines; we will connect NEWSOLAR exclusively with 69kV lines unless we are unable to solve potential contingency violations.
+
 The approach here is to start with the solution involving least total line distance (case 1).
@@
 	\centering
-	\begin{tabular}{|c|l|c|}
+	\begin{tabular}{|c|l|c|r|}
 		\hline
-		\textbf{Case number} & \textbf{Destination buses} & \textbf{Total distance} \\
+		\textbf{Case} & \textbf{Destination} & \textbf{Total} & \textbf{Total Cost} \\
+		\textbf{number} & \textbf{buses} & \textbf{distance (km)} & \textbf{(M\$)} \\
 		\hline
-		1 & BK69, AP69 & 12 \\
-		2 & BK69, OAK69 & 19 \\
-		3 & BK69, OAK138 & 19 \\
-		4 & AP69, OAK69 & 19 \\
-		5 & AP69, OAK138 & 19 \\
-		6 & BK69, PIINE69 & 20 \\
-		7 & BK69, PINE138 & 20 \\
-		8 & AP69, PINE69 & 20 \\
-		9 & AP69, PINE138 & 20 \\
-		10 & BK69, MP69 & 21 \\
-		11 & AP69, MP69 & 21 \\
-		12 & OAK69, PINE69 & 27 \\
-		13 & OAK69, PINE138 & 27 \\
-		14 & OAK138, PINE69 & 27 \\
-		15 & OAK138, PINE138 & 27 \\
-		16 & OAK69, MP69 & 28 \\
-		17 & OAK138, MP69 & 28 \\
-		18 & PINE69, MP69 & 29 \\
-		19 & PINE138, MP69 & 29 \\
+		1 & BK69, AP69 & 12 & 5.94 \\
+		2 & BK69, OAK69 & 19 & 8.53 \\
+		3 & BK69, OAK138 & 19 & 15.17 \\
+		4 & AP69, OAK69 & 19 & 8.53 \\
+		5 & AP69, OAK138 & 19 & 15.17 \\
+		6 & BK69, PIINE69 & 20 & 8.90 \\
+		7 & BK69, PINE138 & 20 & 15.80 \\
+		8 & AP69, PINE69 & 20 & 8.90 \\
+		9 & AP69, PINE138 & 20 & 15.80 \\
+		10 & BK69, MP69 & 21 & 9.27 \\
+		11 & AP69, MP69 & 21 & 9.27 \\
+		12 & OAK69, PINE69 & 27 & 11.49 \\
+		13 & OAK69, PINE138 & 27 & 19.56 \\
+		14 & OAK138, PINE69 & 27 & 19.56 \\
+		15 & OAK138, PINE138 & 27 & 19.56 \\
+		16 & OAK69, MP69 & 28 & 11.86 \\
+		17 & OAK138, MP69 & 28 & 20.19 \\
+		18 & PINE69, MP69 & 29 & 12.23 \\
+		19 & PINE138, MP69 & 29 & 20.82 \\
 		\hline
@@
 	\vspace{0.5em}
-	\caption{Possible NEWSOLAR Connections}
+	\caption{Possible NEWSOLAR Connections with Line Costs (M\$)}
 	\label{tab:all_conn}
 \end{table}
-We started with case 1: maintain NEWSOLAR at 69kV with connections to BUCKEYE and APPLE using Rook 770A conductors.
 
-First we attempted to maintain NEWSOLAR at 69kV with new connections to BUCKEYE and APPLE using Condor 900A/107.5MVA conductors.
-We selected those stations because of their proximity to NEWSOLAR (only 6km each).
-We upgraded the OAK69-BUCKEYE69 and BUCKEYE69-APPLE69 lines to the highest-rated available 69kV conductor (Condor at 900A).
-However, contingency analysis revealed voltage violations at OAK138, dropping to 0.939 per unit when the OAK345-OAK138 transformer is opened.
-This suggests a need for stronger integration with the 138kV network.
-
-Next we installed a 138kV bus at NEWSOLAR with a 138/69kV transformer connecting it to the 69kV bus.
-Since voltage dropped too low at OAK in the previous design, we connected NEWSOLAR138 to OAK138 using Cardinal 1010A/241.4MVA lines.
-Since 138kV lines are significantly more expensive than 69kV, we kept the 69kV connection to PINE69.
-We found a slight overcurrent contingency violation on the OAK69-BUCKEYE69 line when PINE-APPLE is open, so we upgraded it to the 900A Condor lines.
-With this new configuration there are no contingency violations.
-
-PowerWorld's Case Summary for this configuration shows losses of 10.6MW, a 0.1MW decrease from the base scenario.
-That will slightly offset upgrade costs from power saving over five years.
-Contingency analysis showed no violations with this configuration, so we now examine the cost of this approach.
-Table \ref{tab:cost_breakdown_option1} shows the breakdown of costs incurred, with a total of \$20,927,200.
+We found that simply installing connections to BUCKEYE and APPLE results in several contingency violations.
+These violations came from over-currents on the OAK-BUCKEYE line we so we replaced that line with Crow conductors to ensure ample allowance for current.
+With the replaced line we saw no violations.
+The total cost for case 1 with this upgrade is shown in Table \ref{tab:cost_breakdown_case1}.
 \begin{table}[h!]
@@
 		\hline
-		\textbf{Modification} & \textbf{Cost (\$)} \\ \hline
-		\multicolumn{2}{|l|}{\textbf{Replace OAK-BUCKEYE (69kV Condor)}} \\ 
-		\hspace{1em} Fixed Cost & 750,000 \\ 
-		\hspace{1em} Variable Cost (\$410,000/km for 8 km) & 3,280,000 \\ 
-		\hspace{1em} \textbf{Total} & \textbf{4,030,000} \\ \hline
-		\multicolumn{2}{|l|}{\textbf{138-kV Bus/101MVA Transformer}} \\ 
-		\hspace{1em} Bus & 900,000 \\ 
-		\hspace{1em} Transformer & 1,500,000 \\ 
-		\hspace{1em} \textbf{Total} & \textbf{2,400,000} \\ \hline
-		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-OAK138 (138kV Cardinal)}} \\ 
-		\hspace{1em} Fixed Cost & 1,250,000 \\ 
-		\hspace{1em} Variable Cost (\$540,000/km for 13 km) & 7,020,000 \\ 
-		\hspace{1em} \textbf{Total} & \textbf{8,270,000} \\ \hline
-		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-PINE69 (69kV Condor)}} \\ 
-		\hspace{1em} Fixed Cost & 750,000 \\ 
-		\hspace{1em} Variable Cost (\$410,000/km for 14 km) & 5,740,000 \\ 
-		\hspace{1em} \textbf{Total} & \textbf{6,490,000} \\ \hline
-		\textbf{Loss Savings (0.1 MW over 5 years)} & \textbf{-262,800} \\ \hline
-		\textbf{Grand Total} & \textbf{20,927,200} \\ \hline
+		\textbf{Modification} & \textbf{Cost (M\$)} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{Replace OAK-BUCKEYE (69kV Crow)}} \\ 
+		\hspace{1em} Fixed Cost & 0.75 \\ 
+		\hspace{1em} Variable Cost (\$390,000/km for 8 km) & 3.12 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{3.87} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-BUCKEYE (69kV Rook)}} \\ 
+		\hspace{1em} Fixed Cost & 0.75 \\ 
+		\hspace{1em} Variable Cost (\$370,000/km for 6 km) & 2.22 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-APPLE (69kV Rook)}} \\ 
+		\hspace{1em} Fixed Cost & 0.75 \\ 
+		\hspace{1em} Variable Cost (\$370,000/km for 6 km) & 2.22 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
+		\textbf{Grand Total} & \textbf{9.81} \\ \hline
 	\end{tabular}
 	\vspace{0.5em}
-	\caption{Cost Breakdown of Transmission Line and Transformer Upgrades, Including Loss Savings}
-	\label{tab:cost_breakdown_option1}
+	\caption{Cost Breakdown for Case 1 Implementation with OAK-BUCKEYE Upgrade}
+	\label{tab:cost_breakdown_case1}
 \end{table}
 
-The massive expense of replacing lines seen in Table \ref{tab:cost_breakdown_option1} suggests that loss reduction will not pay for more line upgrades.
-Next we examine whether there is a better way to connect NEWSOLAR to the grid, perhaps with closer stations.
+This cost exceeds that of cases 2, 4, 6, 8, 10 and 11 as seen in Table \ref{tab:all_conn}.
+However, the cheapest 6km installation costs \$3M, so for any of these other cases to be preferred there must be no contingency violations.
+If there are, any corrective line replacement will make that option more expensive than case 1 with upgrade.
+
 \section{Conclusion}
 Summary of key findings and recommendations
-
-\begin{thebibliography}{00}
-	\bibitem{b1} PowerWorld Corporation, "PowerWorld Simulator Manual," 2024.
-	\bibitem{b2} IEEE Standard 1547-2018, "IEEE Standard for Interconnection and Interoperability of Distributed Energy Resources with Associated Electric Power Systems Interfaces."
-\end{thebibliography}
-
 \end{document}

### 2024-12-07 paper.tex
draft complete, added slide deck

@@
 	\author{\IEEEauthorblockN{Brent Dickinson}
-		\IEEEauthorblockN{Tianci}
+		\IEEEauthorblockN{Tianci Xi}
 	}
@@
 We need a way to convert the 1-foot spacing parameters appropriately.
-Assuming equilateral spacing of lines, Equation 4.5.9 in the text suggests a simple way to adjust series per-mile impedance from the table:
+Assuming equilateral spacing of lines, Equation 4.5.9 \cite{glover2007} in the text suggests a simple way to adjust series per-mile impedance from the table:
 \begin{flalign}
@@
 \begin{table}
+	\centering
 	\begin{tabular}{|l|c|c|c|}
@@
 Table \ref{tab:all_conn} shows all possible NEWSOLAR connections to the network, given the provided set of right-of-way paths available to us.
-The cost of 138kV lines and transformers suggests we can eliminate any solution involving those lines; we will connect NEWSOLAR exclusively with 69kV lines unless we are unable to solve potential contingency violations.
+We include cost of installing the least expensive conductors (Rook for 69kV, Crow for 138kV) in the last column.
+Note that for any 138kV connections, we need to install a 138kV bus with 69-138 transformer at NEWSOLAR.
+This cost is included in Table \ref{tab:all_conn} and suggests we can eliminate any solution involving those lines; we will connect NEWSOLAR exclusively with 69kV lines unless we are unable to meet the requirements.
 
@@
 		2 & BK69, OAK69 & 19 & 8.53 \\
-		3 & BK69, OAK138 & 19 & 15.17 \\
+		3 & BK69, OAK138 & 19 & 14.37 \\
 		4 & AP69, OAK69 & 19 & 8.53 \\
-		5 & AP69, OAK138 & 19 & 15.17 \\
+		5 & AP69, OAK138 & 19 & 14.37 \\
 		6 & BK69, PIINE69 & 20 & 8.90 \\
-		7 & BK69, PINE138 & 20 & 15.80 \\
+		7 & BK69, PINE138 & 20 & 14.90 \\
 		8 & AP69, PINE69 & 20 & 8.90 \\
-		9 & AP69, PINE138 & 20 & 15.80 \\
+		9 & AP69, PINE138 & 20 & 14.90 \\
 		10 & BK69, MP69 & 21 & 9.27 \\
@@
 		12 & OAK69, PINE69 & 27 & 11.49 \\
-		13 & OAK69, PINE138 & 27 & 19.56 \\
-		14 & OAK138, PINE69 & 27 & 19.56 \\
-		15 & OAK138, PINE138 & 27 & 19.56 \\
+		13 & OAK69, PINE138 & 27 & 18.36 \\
+		14 & OAK138, PINE69 & 27 & 18.36 \\
+		15 & OAK138, PINE138 & 27 & 18.36 \\
 		16 & OAK69, MP69 & 28 & 11.86 \\
-		17 & OAK138, MP69 & 28 & 20.19 \\
+		17 & OAK138, MP69 & 28 & 18.89 \\
 		18 & PINE69, MP69 & 29 & 12.23 \\
-		19 & PINE138, MP69 & 29 & 20.82 \\
+		19 & PINE138, MP69 & 29 & 19.42 \\
 		\hline
@@
 With the replaced line we saw no violations.
-The total cost for case 1 with this upgrade is shown in Table \ref{tab:cost_breakdown_case1}.
+We also saw no violations when we turned off the NEWSOLAR plant in this configuration.
+
+We see significant power loss savings with this configuration.
+The screenshot in Figure \ref{fig:case1loss} demonstrates new losses of 9.8MW, a savings of 0.9MW from the base case.
+To calculate the economic value of this improvement over the five-year period:
+\begin{flalign}
+	\text{Annual hours} &= 365 \text{ days} \times 24 \text{ hours} = 8760 \text{ hours} \\
+	\text{Energy saved} &= 0.9 \text{ MW} \times 8760 \text{ hours/year} \times 5 \text{ years}\nonumber \\
+	&= 39,420 \text{ MWh} \\
+	\text{Cost savings} &= 39,420 \text{ MWh} \times \$60\text{/MWh}\nonumber \\
+	&= \$2.37\text{M}
+\end{flalign}
+The total cost for case 1 with this upgrade (and including the power loss savings) is shown in Table \ref{tab:cost_breakdown_case1}.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/case1loss}
+	\caption{Case summary for case 1 + upgrade}
+	\label{fig:case1loss}
+\end{figure}
+
 \begin{table}[h!]
@@
 		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
-		\textbf{Grand Total} & \textbf{9.81} \\ \hline
+		\textbf{Loss Savings (0.9 MW over 5 years)} & \textbf{-2.37} \\ \hline
+		\textbf{Grand Total} & \textbf{7.44} \\ \hline
 	\end{tabular}
@@
 \end{table}
+We consider cases 2, 4, 6, 8, 10 and 11 as seen in Table \ref{tab:all_conn} because their base cost is in the same neighborhood.
+Since it is difficult to predict power loss savings, due diligence requires at least a cursory examination.
+However, the cheapest 6km installation costs \$3M, so for any of these other cases to be preferred there must be no contingency violations.
+Any corrective line replacement will almost certainly make that option more expensive than case 1 with upgrade.
+Our approach to this analysis was to install all considered lines and alternately turn on or off the relevant lines, shown in Figure \ref{fig:multi}.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/multi}
+	\caption{Approach to multiple connection analysis}
+	\label{fig:multi}
+\end{figure}
 
-This cost exceeds that of cases 2, 4, 6, 8, 10 and 11 as seen in Table \ref{tab:all_conn}.
-However, the cheapest 6km installation costs \$3M, so for any of these other cases to be preferred there must be no contingency violations.
-If there are, any corrective line replacement will make that option more expensive than case 1 with upgrade.
+Case 2 shows four contingency violations related to undervoltage at the OAK 138 \& 345 buses and overcurrent on the BUCKEYE-APPLE line.
+Case 4 shows the same undervolatge violations as case 2.
+Case 6 results in the same overcurrent violation observed in the base case (though only when NEWSOLAR is turned off).
+Cases 8, 10 and 11 all cause overcurrent contingency violations.
+To correct any of these issues, we would need to install a minimum of 6km of Rook conductors.
+That makes all these cases more expensive than case 1 plus upgrade.
+\section{Conclusion}
+Through systematic analysis of 19 possible configurations for the new 75 MW solar facility, we determined that the most cost-effective solution is to connect NEWSOLAR to both BUCKEYE69 and APPLE69 substations using 69 kV lines with Rook conductors, while upgrading the existing OAK69-BUCKEYE69 line using Crow conductors.
+This configuration, costing \$7.44M, represents the optimal balance between reliability requirements and economic constraints.
 
-\section{Conclusion}
-Summary of key findings and recommendations
+The decision to use exclusively 69 kV connections was driven by the substantial cost premium associated with 138 kV options, which required additional substation infrastructure and more expensive conductors.
+While several other 69 kV configurations appeared comparable in cost, all required remedial upgrades to address contingency violations that ultimately made them more costly than our chosen solution.
+The upgrade of the OAK69-BUCKEYE69 line to Crow conductors provides sufficient capacity to handle contingency scenarios both with NEWSOLAR at full output and offline, while maintaining all bus voltages and line flows within acceptable limits.
+
+This design successfully achieves all project objectives: it provides redundant transmission paths to the solar facility, resolves existing system violations, maintains system stability under N-1 contingency conditions, and does so at minimum cost.
+The solution's simplicity and use of standard components should also facilitate maintenance and reduce implementation complexity.
+\begin{thebibliography}{9}
+	\bibitem{glover2007} J. D. Glover, M. S. Sarma, and T. J. Overbye, \textit{Power Systems Analysis and Design}, 4th ed. Stamford, CT: Cengage Learning, 2007.
+\end{thebibliography}
 \end{document}

### 2024-12-09 paper.tex
correct files name
fixed paper and slides for final solution

@@
 	\author{\IEEEauthorblockN{Brent Dickinson}
-		\IEEEauthorblockN{Tianci Xi}
+		\IEEEauthorblockN{Tianci Xie}
 	}
@@
 That makes all these cases more expensive than case 1 plus upgrade.
+
+For due diligence we probed our case 1 + upgrades solution for even more cost effective solutions.
+We discovered that dropping the OAK-BUCKEYE line upgrade but installing a new Rook 69kV line from APPLE to ORANGE improves power loss while requiring only 1 additional km of line.
+This configuration throws no contingency violations with NEWSOLAR on or off.
+Figure \ref{fig:case1plusnewline} shows the lines we installed.
+There are no upgrades outside of installed lines.
+Figure \ref{fig:case1plusnewlineloss} shows a new loss of 9.7MW.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=.7\linewidth]{figures/case1_plusnewline}
+	\caption{Schematic of final solution: case 1 + APPLE-ORANGE`}
+	\label{fig:case1plusnewline}
+\end{figure}
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=1\linewidth]{figures/case1_plusnewline_loss}
+	\caption{Case summary for final solution: case 1 + APPLE-ORANGE}
+	\label{fig:case1plusnewlineloss}
+\end{figure}
+
+Further analysis revealed that this configuration provides several advantages over the previous solution.
+It eliminates the need to replace the existing OAK-BUCKEYE line, reducing construction complexity and avoiding potential service interruptions during upgrades.
+The new APPLE-ORANGE connection creates an alternative power flow path that naturally redistributes power flow during contingencies, resulting in slightly better loss reduction (1.0 MW versus 0.9 MW).
+Table \ref{tab:cost_breakdown_final} demonstrates a modest cost savings over the previous solution, making this our preferred design.
+Table \ref{tab:cost_breakdown_final} demonstrates a slim savings over the previous solution of about \$50k.
+We choose this as our final solution since it meets all other design criteria.
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{|l|r|}
+		\hline
+		\textbf{Modification} & \textbf{Cost (M\$)} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-BUCKEYE (69kV Rook)}} \\ 
+		\hspace{1em} Fixed Cost & 0.75 \\ 
+		\hspace{1em} Variable Cost (\$370,000/km for 6 km) & 2.22 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line NEWSOLAR-APPLE (69kV Rook)}} \\ 
+		\hspace{1em} Fixed Cost & 0.75 \\ 
+		\hspace{1em} Variable Cost (\$370,000/km for 6 km) & 2.22 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{2.97} \\ \hline
+		\multicolumn{2}{|l|}{\textbf{New Line APPLE-ORANGE (69kV Rook)}} \\ 
+		\hspace{1em} Fixed Cost & 0.75 \\ 
+		\hspace{1em} Variable Cost (\$370,000/km for 9 km) & 3.33 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{4.08} \\ \hline
+		\textbf{Loss Savings (1.0 MW over 5 years)} & \textbf{-2.63} \\ \hline
+		\textbf{Grand Total} & \textbf{7.39} \\ \hline
+	\end{tabular}
+	\vspace{0.5em}
+	\caption{Cost Breakdown for Final Solution with APPLE-ORANGE Connection}
+	\label{tab:cost_breakdown_final}
+\end{table}
 \section{Conclusion}
-Through systematic analysis of 19 possible configurations for the new 75 MW solar facility, we determined that the most cost-effective solution is to connect NEWSOLAR to both BUCKEYE69 and APPLE69 substations using 69 kV lines with Rook conductors, while upgrading the existing OAK69-BUCKEYE69 line using Crow conductors.
-This configuration, costing \$7.44M, represents the optimal balance between reliability requirements and economic constraints.
+Through systematic analysis of 19 possible configurations for the new 75 MW solar facility, we determined that the most cost-effective solution is to connect NEWSOLAR to both BUCKEYE69 and APPLE69 substations using 69 kV lines with Rook conductors, while adding a new 69 kV Rook line between APPLE69 and ORANGE69.
+This configuration, costing \$7.39M, represents the optimal balance between reliability requirements and economic constraints.
 
@@
 While several other 69 kV configurations appeared comparable in cost, all required remedial upgrades to address contingency violations that ultimately made them more costly than our chosen solution.
-The upgrade of the OAK69-BUCKEYE69 line to Crow conductors provides sufficient capacity to handle contingency scenarios both with NEWSOLAR at full output and offline, while maintaining all bus voltages and line flows within acceptable limits.
+The addition of the APPLE69-ORANGE69 line provides an alternative power flow path that effectively resolves the existing contingency violations while avoiding the need to upgrade the OAK69-BUCKEYE69 line.
+This configuration maintains stability under all N-1 contingency scenarios both with NEWSOLAR at full output and when offline.
 
 This design successfully achieves all project objectives: it provides redundant transmission paths to the solar facility, resolves existing system violations, maintains system stability under N-1 contingency conditions, and does so at minimum cost.
-The solution's simplicity and use of standard components should also facilitate maintenance and reduce implementation complexity.
+The solution's use of standard components and strategic placement of the new APPLE69-ORANGE69 line not only reduces initial capital costs but also provides better loss reduction, saving an additional 0.1 MW compared to alternative solutions.
+The simplicity of using consistent conductor types (Rook) for all new lines should also facilitate maintenance and reduce implementation complexity.
 \begin{thebibliography}{9}

### 2024-12-09 paper.tex
final change

@@
 For due diligence we probed our case 1 + upgrades solution for even more cost effective solutions.
-We discovered that dropping the OAK-BUCKEYE line upgrade but installing a new Rook 69kV line from APPLE to ORANGE improves power loss while requiring only 1 additional km of line.
+We discovered that dropping the OAK-BUCKEYE line upgrade but installing a new Rook 69kV line from BUCKEYE to ORANGE improves power loss without increasing to total line length.
 This configuration throws no contingency violations with NEWSOLAR on or off.
@@
 There are no upgrades outside of installed lines.
-Figure \ref{fig:case1plusnewlineloss} shows a new loss of 9.7MW.
+Figure \ref{fig:case1plusnewlineloss} shows a new loss of 9.6MW.
 \begin{figure}[h]
@@
 	\includegraphics[width=.7\linewidth]{figures/case1_plusnewline}
-	\caption{Schematic of final solution: case 1 + APPLE-ORANGE`}
+	\caption{Schematic of final solution: case 1 + BUCKEYE-ORANGE`}
 	\label{fig:case1plusnewline}
@@
 	\includegraphics[width=1\linewidth]{figures/case1_plusnewline_loss}
-	\caption{Case summary for final solution: case 1 + APPLE-ORANGE}
+	\caption{Case summary for final solution: case 1 + BUCKEYE-ORANGE}
 	\label{fig:case1plusnewlineloss}
@@
 It eliminates the need to replace the existing OAK-BUCKEYE line, reducing construction complexity and avoiding potential service interruptions during upgrades.
-The new APPLE-ORANGE connection creates an alternative power flow path that naturally redistributes power flow during contingencies, resulting in slightly better loss reduction (1.0 MW versus 0.9 MW).
+The new BUCKEYE-ORANGE connection creates an alternative power flow path that naturally redistributes power flow during contingencies, resulting in slightly better loss reduction (1.1 MW versus 0.9 MW).
 Table \ref{tab:cost_breakdown_final} demonstrates a modest cost savings over the previous solution, making this our preferred design.
-Table \ref{tab:cost_breakdown_final} demonstrates a slim savings over the previous solution of about \$50k.
+Table \ref{tab:cost_breakdown_final} demonstrates a slim savings over the previous solution of about \$0.68m.
 We choose this as our final solution since it meets all other design criteria.
@@
 		\hspace{1em} Fixed Cost & 0.75 \\ 
-		\hspace{1em} Variable Cost (\$370,000/km for 9 km) & 3.33 \\ 
-		\hspace{1em} \textbf{Total} & \textbf{4.08} \\ \hline
-		\textbf{Loss Savings (1.0 MW over 5 years)} & \textbf{-2.63} \\ \hline
-		\textbf{Grand Total} & \textbf{7.39} \\ \hline
+		\hspace{1em} Variable Cost (\$370,000/km for 8 km) & 2.96 \\ 
+		\hspace{1em} \textbf{Total} & \textbf{3.71} \\ \hline
+		\textbf{Loss Savings (1.1 MW over 5 years)} & \textbf{-2.89} \\ \hline
+		\textbf{Grand Total} & \textbf{6.76} \\ \hline
 	\end{tabular}
 	\vspace{0.5em}
-	\caption{Cost Breakdown for Final Solution with APPLE-ORANGE Connection}
+	\caption{Cost Breakdown for Final Solution with BUCKEYE-ORANGE Connection}
 	\label{tab:cost_breakdown_final}
@@
 \section{Conclusion}
-Through systematic analysis of 19 possible configurations for the new 75 MW solar facility, we determined that the most cost-effective solution is to connect NEWSOLAR to both BUCKEYE69 and APPLE69 substations using 69 kV lines with Rook conductors, while adding a new 69 kV Rook line between APPLE69 and ORANGE69.
-This configuration, costing \$7.39M, represents the optimal balance between reliability requirements and economic constraints.
+Through systematic analysis of 19 possible configurations for the new 75 MW solar facility, we determined that the most cost-effective solution is to connect NEWSOLAR to both BUCKEYE69 and APPLE69 substations using 69 kV lines with Rook conductors, while adding a new 69 kV Rook line between BUCKEYE69 and ORANGE69.
+This configuration, costing \$6.76M, represents the optimal balance between reliability requirements and economic constraints.
 
@@
 This design successfully achieves all project objectives: it provides redundant transmission paths to the solar facility, resolves existing system violations, maintains system stability under N-1 contingency conditions, and does so at minimum cost.
-The solution's use of standard components and strategic placement of the new APPLE69-ORANGE69 line not only reduces initial capital costs but also provides better loss reduction, saving an additional 0.1 MW compared to alternative solutions.
+The solution's use of standard components and strategic placement of the new APPLE69-ORANGE69 line not only reduces initial capital costs but also provides better loss reduction, saving an additional 0.2 MW compared to alternative solutions.
 The simplicity of using consistent conductor types (Rook) for all new lines should also facilitate maintenance and reduce implementation complexity.
